\section{Methodology}\label{methodology}

The UCI Diabetes 130-US hospitals (1999–2008) dataset is a publicly available dataset. It contains both numerical and categorical features. Additionally, 
there are many columns with missing data as well as duplicate rows. Logistic regression expects numerical values as input features. As a result it 
is important to clean the data before it can be used.

\subsection{Data Cleaning}\label{data_cleaning}

Firstly, duplicate rows and empty columns were handled. The dataset was ordered in ascending order using the 'encounter\_id' column. Thereafter, the smallest 'encounter\_id' for a specific 'patient\_nbr'
was removed. This was also done with the intention to use the 'encounter\_id' column to perform time-aware splitting during the experiment as mentioned in Section \ref{splitting}. Thereafter, missing values were handled. 
It was observed that the 'weight' column was largely unpopulated. As a result this column was dropped. The next column with the biggest amount of missing values was the
'payer\_code' column. The 'payer\_code' column was dropped as logically this column has no statistical importance on determining whether a patient readmits or not.
Thereafter, the last three columns with missing values were dealt with: 'race', 'medical\_speciality', 'diag\_1', 'diag\_2' and 'diag\_3'. These three column required some form of
imputation as all three columns were statistically important. The imputation for each of these columns were built into a custom \emph{DataCleaner} class that is called in the pipeline setup
so that when the imputation is performed, only insights learned from the training data is used to impute missing values in the train, validation and test sets respectively. This was done to prevent data 
leakage. Since the 'race' column only contained a small portion of missing values, these values were imputed using the highest probability of the 'race' column within the train set. 
Next, missing values in the 'medical speciality' column were classified as 'missing'. This column had over 70 categories, therefore, only the top 10 categories were selected, with the 
rest of data termed as 'other'. Lastly, the 'diag\_1', 'diag\_2' and 'diag\_3' column's missing values were imputed using the most common category in each column. Additionally, there were also
over 700 categories in each column which was then converted using frequency encoding.

After dealing with duplicate rows and missing values, categorical variables that did not need one-hot encoding were handled. Firstly, the 'age' column was converted to numerical values 
by taking the mean of the age range. Next, columns with single-valued categories were dropped. Thereafter, binary columns were converted to 0/1. Lastly, the target column 'readmitted' 
was converted to a binary column where 1 represented readmission within 30 days and 0 represented no readmission within 30 days.

\subsection{Model Creation}

After the data was cleaned, the model was created using a pipeline. Firstly, in the pipeline the columns in need of imputation were handled by the \emph{DataCleaner} class as mentioned
in the Section \ref{data_cleaning}. Thereafter, a column transformer was used to normalize all numerical columns and one-hot encode all categorical columns. This base framework was then used 
for the various initial tests as well as for hyperparameter tuning. 

